# Reproducible Research: Peer Assessment 1

pelase download ziped data from:
  [http://github.com/mdrzazga/RepData_PeerAssessment1/raw/master/activity.zip]

## Loading and preprocessing the data
```{r}
activity.z <- unz("activity.zip","activity.csv")
setAs("character","myDate", function(from) as.Date(from, format="%Y-%m-%d") )
activity <- read.csv(activity.z, colClasses=c("integer","myDate","integer"), na.strings="NA")
str(activity)
```


## What is mean total number of steps taken per day?

```{r}
activity.day <- tapply(activity$steps, activity$date, sum)
hist(activity.day)
summary(activity.day)
avr <- mean(activity.day,na.rm=T)
med <- median(activity.day,na.rm=T)
```
more precisely: mean = `r avr` and mediana = `r med`
## What is the average daily activity pattern?
```{r}
activity.interval <- aggregate(activity$steps, list(activity$interval), mean, na.rm=T)
plot( activity.interval$Group.1, activity.interval$x, type="l", xlab="interval", ylab="average number of steps taken")

maxStepsInterval <- activity.interval[which.max(activity.interval$x),1]

```
We have maximum at `r maxStepsInterval` interval .

## Imputing missing values
```{r}
cc <- complete.cases(activity)
```
There are `r sum(!cc)` missing values in the dataset (i.e. the total number of rows with NAs).
We will update missing value using mean for that 5-minute interval from active.interval and stor it in activity.clean dataframe.
```{r}
activity.clean <- activity
for(i in 1: nrow(activity.clean)){ 
  if(is.na(activity.clean[i,1])){
    activity.clean[i,1]<- activity.interval[activity.interval$Group.1==activity[i,3],2]
    }
  }
str(activity.clean)
sum(!complete.cases(activity.clean))
activity.clean.day <- tapply(activity.clean$steps, activity.clean$date, sum)
hist(activity.clean.day)
summary(activity.clean.day)
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
# for international issue
Sys.setlocale("LC_TIME","en_GB.UTF-8")
library(lattice)
activity$dayclass <- ifelse(weekdays(activity$date) %in% c("Saturday","Sunday"), "weekend", "weekday")
activity.interval4dayclass <-aggregate(list(steps=activity$steps), list(dayclass = activity$dayclass, interval = activity$interval), mean, na.rm=T)

xyplot(steps ~ interval | dayclass, data = activity.interval4dayclass, layout = c(1, 2), type="l", ylab="Number of steps")

```
